Turned on!": Momentum in Round-Based First Person Shooter Esports

### 2022-07-18 presentation.qmd
cooler title

---
title: "Streaking and Clutching in Round-Based First Person Shooter Esports"
author: "Tony ElHabr"
format:
  revealjs:
    slide-number: true
    incremental: false
    theme: [dark, theme.scss]
execute: 
  include: false
  echo: false
  eval: false
---

>>>>

---
title: '"Turned on!": Momentum in Round-Based First Person Shooter Esports'
author: 'Tony ElHabr'
format:
  revealjs:
    slide-number: true
    incremental: false
    theme: [dark, theme.scss]
execute: 
  include: false
  echo: false
  eval: false
---
